Empirical Study of Scientific Computer Software: Objectives and Research Questions

### 2020-06-17 OverallResearchProposal/ObjectivesAndResearchQuestions.tex
Further edits, nothing major

Focused on a single problem or issue
Researchable using primary and/or secondary sources
Feasible to answer within the timeframe and practical constraints
Specific enough to answer thoroughly
Complex enough to develop the answer over the space of a paper or thesis
Relevant to your field of study and/or society more broadly

>>>>

\begin{itemize}
\item Focused on a single problem or issue
\item Researchable using primary and/or secondary sources
\item Feasible to answer within the timeframe and practical constraints
\item Specific enough to answer thoroughly
\item Complex enough to develop the answer over the space of a paper or thesis
\item Relevant to your field of study and/or society more broadly
\end{itemize}
